Formalizing Stack Safety as a Security Property

### 2023-02-04 submission5/core.tex
Mostly figures

Other mechanisms besides these should also be amenable to strong
formal guarantees.  In particular, Roessler and DeHon
\cite{DBLP:conf/sp/RoesslerD18} have presented an array of tag-based
micro-policies~\cite{pump_oakland2015} for stack safety that offer
strong guarantees.  Their most realistic micro-policy, called Lazy
Tagging and Clearing (\(LTC\)), makes an interesting performance
trade-off: it allows function activations to improperly write into one
another's stack frames, but ensures that the owner of the corrupted
memory cannot access it afterward.

Under this policy, one function activation {\em can} corrupt another's
memory---just not in ways that do not affect observable behavior.
Therefore, \(LTC\) would not fulfill Georges et al.'s property
(appropriately adapted to the tagged setting).  But \(LTC\) does
arguably enforce stack safety.  A looser, more observational
definition of stack safety is needed to fit this situation.

We propose here a formal characterization of stack safety, based on
the intuition of protecting function activations from each other.
\bcp{Aren't other formal definitions based on the same intuition?}
We use the tools of language-based
security~\cite{sabelfeld2003language}, decomposing stack safety into a family of
properties describing
the {\em integrity} and {\em confidentiality} of the caller’s local state
and the callee's behavior during the callee's execution, plus the
{\em well-bracketed control flow} (\(\wbcf\)) property articulated by
Skorstengaard et al.~\cite{SkorstengaardSTKJFP}.
While our properties are motivated by the desire to specify \(LTC\) precisely,
they are stated abstractly in hopes that they may also apply
to other enforcement mechanisms.

We find, via property-based random testing, that \(LTC\) is flawed in
a way that undermines both integrity and confidentiality; after
correcting this flaw, the repaired \(LTC\) satisfies all our
properties.  Moreover, we show that our properties can be extended to
describe calling conventions with features such as callee-save
registers, argument-passing on the stack, and tail-call
elimination. We modify \(LTC\) to protect these features and apply
random testing to validate this extended protection mechanism against
the extended properties.

@@

\bcp{Agreed.  I think in particular the first paragraph can just go.
  But this is not enough.  Also, the section is trying to do at least
  two things---talk about earlier work and how we compare, and talk
  about why we believe a flexible approach is good.  The whole
  discussion is a bit wooly and confusing.}

@@

\begin{itemize}
\item We give a novel characterization of stack safety as a collection
of properties: confidentiality and integrity for callee and caller,
plus well-bracketed control-flow. Different subsets of these
properties characterize the security guarantees offered by mechanisms
that support only some aspects of stack safety\bcp{where do we show
  this?}.  The properties they are parameterized over a notion of
external observation, allowing them to characterize lazy enforcement
mechanisms.
\item We instantiate\bcp{extend??} these definitions in a realistic
setting with features such as\bcp{``such as''? are there others?}
argument passing on the stack, callee-saves registers, and tail-call
elimination.\bcp{How about: We extend these core definitions to
  describe a realistic setting with argument passing on the stack,
  callee-saves registers, and tail-call elimination.}  Our model is
modular enough that handling these features is straightforward.
\bcp{Throughout, the way we talk about the ``core model'' and its
  intantiation / extension / enrichment with realistic features feels
  quite weasily.}
\item We validate a tag-based enforcement mechanism, \emph{Lazy
  Tagging and Clearing}, via property-based random testing, find that
it falls short, and propose and validate a fix.
\end{itemize}

In the next section, we give a brief overview of the structure of
properties.  In \cref{sec:example}, we walk through a function call in
a simple example machine and discuss how each of our properties
applies to it, informally. In the process we motivate the properties
from a security perspective.
%
In \cref{sec:formal} we formalize the machine model,
its {\em security semantics}, and the stack safety properties built on these.
In \Cref{sec:enforcement} we describe the micro-policies that we test,
in \cref{sec:testing} the testing framework itself, and in
\cref{sec:relwork,sec:future} related and future work.

The accompanying artifact contains formal definitions (in Coq) of our
properties, plus our testing framework.  It does not include proofs:
we use Coq primarily for the QuickChick testing library and for
ensuring that our definitions are unambiguous.  Formal proofs are left
as future work.

@@

When our properties are used to evaluate a system, the threat model
will depend on the details of that system. However, there are some
constraints that our design puts on any system. In particular, we must
trust that the method of distinguishing security-relevant operations
is accurate.  For example, if the enforcement mnechanism involves
labels placed on code by a compiler, we must trust that the compiler
placed those labels correctly. For instance, if a compiled function
call is not marked as such, then the caller's data might not be
protected from the callee.  Conversely, marking too many operations as
calls might mean that the property becomes too strong to be
enforced.\bcp{I don't understand that---wouldn't it mean that
  enforcing the property causes almost all programs to be rejected?
  (I.e., isn't it a case of false negatives rather than false
  positives?)}

\bcp{Still working here:}

We do not assume that low-level code adheres to any fixed calling
convention or implements any particular source-language constructs.
Indeed, if the source
language is C, then high-level programs might contain undefined
behavior, in which case they might be compiled to arbitrary machine
code. A given enforcement 
mechanism or target architecture might place additional constraints, particularly on the behavior of
call and return sequences. For instance, extant implementations tend to assume
implicitly that callee-saved registers have their values maintained by whichever compiler
generated their code. Our properties explicitly state this as a requirement,
which could be enforced by a micro-policy, a well-behaved compiler, or other enforcement technique.
Roessler and DeHon include the compiler in their trusted computing
base, so our properties 
are stronger than necessary to characterize their micro-policies.

In general, it is impossible to distinguish buggy machine code from an
attacker.  In our examples we will identify one function or another as
an attacker, but we do not require any static division between trusted
and untrusted code, and we aim to protect even buggy code.

This is a strong threat model, but it does omit some important aspects
of stack safety in real systems: in particular, it does not address
concurrency.  Hardware and timing attacks are also out of scope.
%

@@

\newcommand{\freebox}[1][10pt]{\tikz \filldraw[fill=blue] (0,0) rectangle (#1,#1);}
\newcommand{\pubbox}[1][10pt]{\tikz \filldraw[fill=lightgray] (0,0) rectangle (#1,#1);}
\newcommand{\objbox}[1][10pt]{\tikz \filldraw[fill=yellow] (0,0) rectangle (#1,#1);}
\newcommand{\sealbox}[1][10pt]{\tikz \filldraw[fill=red] (0,0) rectangle (#1,#1);}

\newcommand{\textbox}[1][]{\tikz \filldraw[fill=lightgray] (0,0) rectangle (30pt,30pt) node[pos=.5]{#1};}
\newcommand{\numbox}[1][]{\tikz \filldraw[fill=lightgray] (0,0) rectangle (20pt,20pt) node[pos=.5]{#1};}
\newcommand{\leftbox}[1][]{\tikz \filldraw[fill=blue!20] (0,0) rectangle (20pt,20pt) node[pos=.5]{#1};}
\newcommand{\rightbox}[1][]{\tikz \filldraw[fill=orange!20] (0,0) rectangle (20pt,20pt) node[pos=.5]{#1};}

\begin{figure}
  \begin{subfigure}{\columnwidth}
    {\tt
      volatile int out;

@@

      \}}
  \end{subfigure}
  \begin{subfigure}{\columnwidth}
    \begin{tabular}{r l | l}
      \labeledrow{0:}{addi sp,sp,-20}{\(\mathbf{alloc} ~ (-20,20)\)}
      \labeledrow{4:}{sd ra,12(sp)}{}
      \labeledrow{8:}{sw a0,8(sp)}{}
      \labeledrow{12:}{sw zero,4(sp)}{}
      \labeledrow{16:}{jal f,ra}{\(\mathbf{call} ~ \emplist \)}
      \labeledrow{20:}{sw a0,0(sp)}{}
      \labeledrow{24:}{lw a4,4(sp)}{}
      \labeledrow{28:}{li a5,42}{}
      \labeledrow{32:}{bne a4,a5,L1}{}
      \labeledrow{36:}{lw a0,8(sp)}{}
      \labeledrow{40:}{sw a0,out}{}
      \labeledrow{44:}{j L2:}{}
      \labeledrow{L1, 48:}{lw a0,0(sp)}{}
      \labeledrow{52:}{sw a0,out}{}
      \labeledrow{L2, 56:}{ld ra,12(sp)}{}
      \labeledrow{60:}{addi sp,sp,20}{\(\mathbf{dealloc} ~ (0,20)\)}
      \labeledrow{64:}{jalr ra}{\(\mathbf{return}\)}
    \end{tabular}
  \end{subfigure}
  \begin{subfigure}{\columnwidth}
    \center
    \vspace{\abovedisplayskip}
    \(\textnormal{\large \dots} \pubbox[30pt] \!\! \stackrel{\textsc{\normalsize sp}}{\textbox[\tt res]}
    \stackrel{\textsc{\normalsize 4(sp)}}{\textbox[\tt sens]}
    \stackrel{\textsc{\normalsize 8(sp)}}{\textbox[\tt sec]}
    \stackrel{\textsc{\normalsize 12(sp)} \hfill}{\textbox[\(\mathtt{ra_1}\)]\textbox[\(\mathtt{ra_2}\)]}
    \textnormal{\large \dots}\)
  \end{subfigure}

@@

\begin{figure}
  \centering
  \[
  \stackrel{\texttt{res}}{\numbox[0]}
  \stackrel{\texttt{sens}}{\numbox[0]}
  \stackrel{\texttt{sec}}{\numbox[5]}
  \stackrel{\texttt{ra}}{\numbox[0]\numbox[0]}\]
  %
  \[\big\Downarrow\]
  %
  \[
  \stackrel{\texttt{res}}{\numbox[0]}
  \stackrel{\texttt{sens}}{\numbox[\bf 42]}
  \stackrel{\texttt{sec}}{\numbox[5]}
  \stackrel{\texttt{ra}}{\numbox[0]\numbox[0]}\]
  %
  \[\overbrace{
    \stackrel{\texttt{res}}{\numbox[0]}
    \stackrel{\texttt{sens}}{\numbox[\bf 42]}
    \stackrel{\texttt{sec}}{\numbox[5]}
    \stackrel{\texttt{ra}}{\numbox[0]\numbox[0]}
    \hspace{1cm}
    \stackrel{\texttt{res}}{\numbox[0]}
    \stackrel{\texttt{sens}}{\numbox[\bf 0]}
    \stackrel{\texttt{sec}}{\numbox[5]}
    \stackrel{\texttt{ra}}{\numbox[0]\numbox[0]}}\]
  \[\large\hookrightarrow 5 \hspace{1cm} \large\hookrightarrow 1\]

@@

\begin{figure}
    \centering
    \[
    \stackrel{\texttt{res}}{\numbox[0]}
    \stackrel{\texttt{sens}}{\numbox[0]}
    \stackrel{\texttt{sec}}{\numbox[5]}
    \stackrel{\texttt{ra}}{\numbox[0]\numbox[0]}\]
    %
    \[\overbrace{
    \stackrel{\texttt{res}}{\leftbox[0]}
    \stackrel{\texttt{sens}}{\leftbox[0]}
    \stackrel{\texttt{sec}}{\leftbox[5]}
    \stackrel{\texttt{ra}}{\leftbox[0]\leftbox[0]}
    \hspace{1cm}
    %
    \stackrel{\texttt{res}}{\rightbox[2]}
    \stackrel{\texttt{sens}}{\rightbox[3]}
    \stackrel{\texttt{sec}}{\rightbox[4]}
    \stackrel{\texttt{ra}}{\rightbox[5]\rightbox[6]}}
    \]
    \[\large\Downarrow \hspace{1cm} \large\hookrightarrow 5 \hspace{0.5cm} \not \approx \hspace{0.5cm}
    \large\hookrightarrow 4 \hspace{1cm} \large\Downarrow\]
    \[
    \stackrel{\texttt{res}}{\leftbox[\textbf{0}]}
    \stackrel{\texttt{sens}}{\leftbox[0]}
    \stackrel{\texttt{sec}}{\leftbox[5]}
    \stackrel{\texttt{ra}}{\leftbox[0]\leftbox[0]}
    \hspace{1cm}
    %
    \stackrel{\texttt{res}}{\rightbox[\textbf{2}]}
    \stackrel{\texttt{sens}}{\rightbox[3]}
    \stackrel{\texttt{sec}}{\rightbox[4]}
    \stackrel{\texttt{ra}}{\rightbox[5]\rightbox[6]}
    \]

@@

To illustrate the issues, note that {\tt f} has also stored a 0 below the stack pointer.
%
\begin{figure}
    \centering
    \[
    \stackrel{\texttt{res}}{\numbox[0]}
    \stackrel{\texttt{sens}}{\numbox[0]}
    \stackrel{\texttt{sec}}{\numbox[5]}
    \stackrel{\texttt{ra}}{\numbox[0]\numbox[0]}\]
    %
    \[\overbrace{
    \stackrel{\texttt{res}}{\leftbox[0]}
    \stackrel{\texttt{sens}}{\leftbox[0]}
    \stackrel{\texttt{sec}}{\leftbox[5]}
    \stackrel{\texttt{ra}}{\leftbox[0]\leftbox[0]}
    \hspace{1cm}
    %
    \stackrel{\texttt{res}}{\rightbox[2]}
    \stackrel{\texttt{sens}}{\rightbox[3]}
    \stackrel{\texttt{sec}}{\rightbox[4]}
    \stackrel{\texttt{ra}}{\rightbox[5]\rightbox[6]}}
    \]
    \[\large\Downarrow \hspace{1cm} \mathtt{a0} \leftbox[0] \hspace{1cm}
    \rightbox[7] \mathtt{a0} \hspace{1cm} \large\Downarrow\]
    \[
    \stackrel{\texttt{res}}{\leftbox[0]}
    \stackrel{\texttt{sens}}{\leftbox[0]}
    \stackrel{\texttt{sec}}{\leftbox[5]}
    \stackrel{\texttt{ra}}{\leftbox[0]\leftbox[0]}
    \hspace{1cm}
    %
    \stackrel{\texttt{res}}{\rightbox[2]}
    \stackrel{\texttt{sens}}{\rightbox[3]}
    \stackrel{\texttt{sec}}{\rightbox[4]}
    \stackrel{\texttt{ra}}{\rightbox[5]\rightbox[6]}
    \]
    \[\mathtt{a0} \leftbox[0] \hspace{1cm}
    \mathtt{a0} \rightbox[0]\]
  \caption{Return-time Confidentiality Violation}
  \label{fig:variant3}
\end{figure}
%
Now consider three elements: the address \(\SP - 4\), the address \(\SP + 12\),
and the register {\tt a0}. The execution from the right-hand state to its return
has changed the value at \(\SP - 4\), but that value matches that of the
left-hand variant at its return. Therefore, the change does not represent a leak.

>>>>

Fortunately, other mechanisms besides these should be
amenable to strong 
formal guarantees.  In particular, 
Roessler and DeHon \cite{DBLP:conf/sp/RoesslerD18} have presented an
array of tag-based micro-policies~\cite{pump_oakland2015} for stack
safety that give strong guarantees.
Their most realistic micro-policy, called Lazy Tagging and Clearing (\(LTC\)),
makes an interesting performance trade-off: it allows function
activations to improperly write into one another's stack frames, but ensures that the owner of the corrupted memory cannot access
it afterward.

Because memory does get corrupted, \(LTC\) would not fulfill an
adaptation of Georges et al.'s property to the tagged setting.  But
there is a useful sense in which \(LTC\) does enforce stack safety.
While it does not necessarily protect individual addresses on the
stack, it does prevent one function activation from interfering with
another's observable behavior.

We propose a formal characterization of stack safety based on the intuition
of protecting each function activation from other activations.
We use the formal tools of language-based
security~\cite{sabelfeld2003language}, decomposing stack safety into a family of
properties describing
the {\em integrity} and {\em confidentiality} of the caller’s local state
and the callee's behavior during the callee's execution, plus the control-flow protection
of {\em well-bracketed control flow} (\(\wbcf\)) articulated by
Skorstengaard et al.~\cite{SkorstengaardSTKJFP}.
While our properties are motivated by the desire to specify \(LTC\) precisely, 
they are stated somewhat abstractly in hopes that they may be applicable
to other enforcement mechanisms.

The structure of our properties enables them to be easily extended\bcp{??} to characterize systems with
features such as callee-save registers, argument-passing on the stack,
and tail-call elimination. We likewise extend \(LTC\) to protect these features, and
test the extended micro-policy against our property. We find that, apart from the extensions, \(LTC\)
is flawed in a way that undermines integrity and confidentiality, and we correct
this flaw.

@@

@@

\begin{itemize}
\item A novel characterization of stack safety as a collection of properties:
  confidentiality and integrity for callee and caller, and well-bracketed
  control-flow. These can characterize the security requirements of systems
  that support only some portion of stack safety, and are
  parameterized over a notion of external observation, so that they can characterize
  lazy enforcement.
\item An instantiation of these definitions in a realistic
  setting with features such as argument passing
  on the stack, callee-saves registers, and tail-call elimination.
  Our model is modular enough that handling these features is straightforward.
\item The validation, via property-based randomize testing, of tag-based
  stack-safety policies. We find that \emph{Lazy Tagging and Clearing}
  falls short of stack safety, and propose a fix.
\end{itemize}

Our artifact contains Coq formalizations of our properties for illustrative purposes
as well as their testing implementation. There are no proofs---we use Coq primarily
for the QuickChick library and to ensure that the formalizations are unambiguous.
Formal proofs are left as future work.

@@

When our properties are used to evaluate a system, the threat model will depend on the
details of that system. However, there are some constraints that our design puts on
any system. We must trust that the method of distinguishing security-relevant operations is accurate; if it
involves labels placed on code by a compiler, that means trusting that the compiler placed
those labels correctly. If operations occur that are not recognized, those operations
might not be guaranteed to protect their principals---for instance, an unlabeled call
might not protect the caller's data from the callee. On the flip side, applying an incorrect
label most likely means that the property becomes too strong to be enforced.

Otherwise, we do not assume that the code adheres to any particular
calling convention or implements a source language construct.
In particular, while we are agnostic as to the source
language, we certainly aim to support C, and so any source function might contain undefined
behavior resulting in its compilation to arbitrary machine code. A given enforcement
mechanism or target architecture might place additional constraints, particularly on the behavior of
call and return sequences. For instance, extant implementations tend to assume
implicitly that callee-saved registers have their values maintained by whichever compiler
generated their code. Our properties explicitly state this as a requirement,
which could be enforced by a micro-policy, a well-behaved compiler, or other enforcement technique.
Roessler and DeHon have the compiler in their trusted computing base, so our properties
are stronger than necessary to characterize their micro-policies.

In general, it is impossible to distinguish buggy machine code from an attacker; in
our examples we will identify one function or another as an attacker, but we do not
require any static division between trusted and untrusted code, and we aim to protect
even buggy code.

This is a strong threat model, but it does omit some important aspects of
security enforcement: in particular, hardware and timing attacks are out of scope, and
we do not address concurrency---that is a high-priority future work.
%

\paragraph*{Organization}

In the next section, we will give a brief overview of the structure of properties.
Then in \cref{sec:example}, we will walk through a function
call in a simple example machine and discuss how each of our properties applies to it,
informally. In the process we discuss some motivation for the properties, from a security
perspective.

In \cref{sec:formal} we formalize the machine model, 
its {\em security semantics}, and the stack safety properties built on these. 
\Cref{sec:enforcement} describes the micro-policies that we test,
\cref{sec:testing} the testing framework itself, and
\cref{sec:relwork,sec:future} discuss related and future work.

@@

\begin{figure}
  \newcommand{\figonebox}[1][]{\genbox{30px}{lightgray}{#1}}
  \begin{subfigure}{\columnwidth}
    {\tt
      volatile int out;

@@

      \}}
  \end{subfigure}
  \begin{subfigure}{\columnwidth}
    \begin{tabular}{r l | l}
      \labeledrow{0:}{addi sp,sp,-20}{\(\mathbf{alloc} ~ (-20,20)\)}
      \labeledrow{4:}{sd ra,12(sp)}{}
      \labeledrow{8:}{sw a0,8(sp)}{}
      \labeledrow{12:}{sw zero,4(sp)}{}
      \labeledrow{16:}{jal f,ra}{\(\mathbf{call} ~ \emplist \)}
      \labeledrow{20:}{sw a0,0(sp)}{}
      \labeledrow{24:}{lw a4,4(sp)}{}
      \labeledrow{28:}{li a5,42}{}
      \labeledrow{32:}{bne a4,a5,L1}{}
      \labeledrow{36:}{lw a0,8(sp)}{}
      \labeledrow{40:}{sw a0,out}{}
      \labeledrow{44:}{j L2:}{}
      \labeledrow{L1, 48:}{lw a0,0(sp)}{}
      \labeledrow{52:}{sw a0,out}{}
      \labeledrow{L2, 56:}{ld ra,12(sp)}{}
      \labeledrow{60:}{addi sp,sp,20}{\(\mathbf{dealloc} ~ (0,20)\)}
      \labeledrow{64:}{jalr ra}{\(\mathbf{return}\)}
    \end{tabular}
  \end{subfigure}
  \begin{subfigure}{\columnwidth}
    \center
    \vspace{\abovedisplayskip}
    \(\xleftarrow{\figonebox[\dots] \stackrel{\textsc{\normalsize sp}}{\figonebox[\tt res]}
    \stackrel{\textsc{\normalsize 4(sp)}}{\figonebox[\tt sens]}
    \stackrel{\textsc{\normalsize 8(sp)}}{\figonebox[\tt sec]}
    \stackrel{\textsc{\normalsize 12(sp)} \hfill}{\figonebox[\(\mathtt{ra_1}\)]\figonebox[\(\mathtt{ra_2}\)]}
    }\)
  \end{subfigure}

@@

\newcommand{\figfourbox}[1][]{\genbox{20px}{red}{#1}}

\begin{figure}
  \centering
  \[
  \stackrel{\texttt{res}}{\figfourbox[0]}
  \stackrel{\texttt{sens}}{\figfourbox[0]}
  \stackrel{\texttt{sec}}{\figfourbox[5]}
  \stackrel{\texttt{ra}}{\figfourbox[0]\figfourbox[0]}\]
  %
  \[\big\Downarrow\]
  %
  \[
  \stackrel{\texttt{res}}{\figfourbox[0]}
  \stackrel{\texttt{sens}}{\genbox{20px}{red!50}{\bf 42}}
  \stackrel{\texttt{sec}}{\figfourbox[5]}
  \stackrel{\texttt{ra}}{\figfourbox[0]\figfourbox[0]}\]
  %
  \[\overbrace{
    \stackrel{\texttt{res}}{\figfourbox[0]}
    \stackrel{\texttt{sens}}{\genbox{20px}{\leftvariant}{\bf 42}}
    \stackrel{\texttt{sec}}{\figfourbox[5]}
    \stackrel{\texttt{ra}}{\figfourbox[0]\figfourbox[0]}
    \hspace{1cm}
    \stackrel{\texttt{res}}{\figfourbox[0]}
    \stackrel{\texttt{sens}}{\genbox{20px}{\rightvariant}{\bf 0}}
    \stackrel{\texttt{sec}}{\figfourbox[5]}
    \stackrel{\texttt{ra}}{\figfourbox[0]\figfourbox[0]}}\]
  \[\stackrel{\(\hookrightarrow \mathtt{out}}{\genbox{20px}{white}{5}} \hspace{0.5cm}
  \raisebox{\height}{\not\approx}
  \hspace{0.5cm}
  \stackrel{\(\hookrightarrow \mathtt{out}}{\genbox{20px}{white}{1}}\]

@@

\newcommand{\leftbox}[1][]{\genbox{20px}{\leftvariant}{#1}}
\newcommand{\rightbox}[1][]{\genbox{20px}{\rightvariant}{#1}}

\begin{figure}
    \centering
    \[
    \stackrel{\texttt{res}}{\figfourbox[0]}
    \stackrel{\texttt{sens}}{\figfourbox[0]}
    \stackrel{\texttt{sec}}{\figfourbox[5]}
    \stackrel{\texttt{ra}}{\figfourbox[0]\figfourbox[0]}\]
    %
    \[\overbrace{
    \stackrel{\texttt{res}}{\leftbox[0]}
    \stackrel{\texttt{sens}}{\leftbox[0]}
    \stackrel{\texttt{sec}}{\leftbox[5]}
    \stackrel{\texttt{ra}}{\leftbox[0]\leftbox[0]}
    \hspace{1cm}
    %
    \stackrel{\texttt{res}}{\rightbox[2]}
    \stackrel{\texttt{sens}}{\rightbox[3]}
    \stackrel{\texttt{sec}}{\rightbox[4]}
    \stackrel{\texttt{ra}}{\rightbox[5]\rightbox[6]}}
    \]
    \[\raisebox{.5\height}{\Bigg\Downarrow} \hspace{1cm}
    \stackrel{\(\hookrightarrow \mathtt{out}}{\genbox{20px}{white}{5}} \hspace{0.5cm}
    \raisebox{\height}{\not\approx}
    \hspace{0.5cm}
    \stackrel{\(\hookrightarrow \mathtt{out}}{\genbox{20px}{white}{4}} \hspace{1cm}
    \raisebox{.5\height}{\Bigg\Downarrow}\]
    \[
    \stackrel{\texttt{res}}{\leftbox[0]}
    \stackrel{\texttt{sens}}{\leftbox[0]}
    \stackrel{\texttt{sec}}{\leftbox[5]}
    \stackrel{\texttt{ra}}{\leftbox[0]\leftbox[0]}
    \hspace{1cm}
    %
    \stackrel{\texttt{res}}{\rightbox[2]}
    \stackrel{\texttt{sens}}{\rightbox[3]}
    \stackrel{\texttt{sec}}{\rightbox[4]}
    \stackrel{\texttt{ra}}{\rightbox[5]\rightbox[6]}
    \]

@@

To illustrate the issues, note that {\tt f} has also stored a 0 below the stack pointer.
%
\begin{figure}
    \centering
    \[
    \stackrel{\texttt{res}}{\figfourbox[0]}
    \stackrel{\texttt{sens}}{\figfourbox[0]}
    \stackrel{\texttt{sec}}{\figfourbox[5]}
    \stackrel{\texttt{ra}}{\figfourbox[0]\figfourbox[0]}\]
    %
    \[\overbrace{
    \stackrel{\texttt{res}}{\leftbox[0]}
    \stackrel{\texttt{sens}}{\leftbox[0]}
    \stackrel{\texttt{sec}}{\leftbox[5]}
    \stackrel{\texttt{ra}}{\leftbox[0]\leftbox[0]}
    \hspace{1cm}
    %
    \stackrel{\texttt{res}}{\rightbox[2]}
    \stackrel{\texttt{sens}}{\rightbox[3]}
    \stackrel{\texttt{sec}}{\rightbox[4]}
    \stackrel{\texttt{ra}}{\rightbox[5]\rightbox[6]}}
    \]
    \[\large\Downarrow \hspace{1cm} \mathtt{a0} \leftbox[0] \hspace{1cm}
    \rightbox[7] \mathtt{a0} \hspace{1cm} \large\Downarrow\]
    \[
    \stackrel{\texttt{res}}{\leftbox[0]}
    \stackrel{\texttt{sens}}{\leftbox[0]}
    \stackrel{\texttt{sec}}{\leftbox[5]}
    \stackrel{\texttt{ra}}{\leftbox[0]\leftbox[0]}
    \hspace{1cm}
    %
    \stackrel{\texttt{res}}{\rightbox[2]}
    \stackrel{\texttt{sens}}{\rightbox[3]}
    \stackrel{\texttt{sec}}{\rightbox[4]}
    \stackrel{\texttt{ra}}{\rightbox[5]\rightbox[6]}
    \]
    \[\mathtt{a0} \leftbox[0] \hspace{1cm}
    \mathtt{a0} \rightbox[0]\]
  \caption{Return-time Confidentiality Violation}
  \label{fig:variant3}
\end{figure}
%
Now consider three elements: the address \(\SP - 4\), the address \(\SP + 12\),
and the register {\tt a0}. The execution from the right-hand state to its return
has changed the value at \(\SP - 4\), but that value matches that of the
left-hand variant at its return. Therefore, the change does not represent a leak.
